Supplimentary Analysis

### 2021-11-17 Supplymentary.Rmd
adding Geographic location table to Supplements (still needs work in the formatting)

>>>>

# Geographic Locations of Survey Participants
```{r TzTable, include=FALSE, warning=F,message=FALSE}
descriptives.data%>%
  tbl_summary(
    label = slypos_demographics_tz.factor ~ "Time zone - Country",
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no",
    sort = all_categorical() ~ "frequency",
    include = "slypos_demographics_tz.factor"
  )  %>% bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_caption("Geographical Location") -> tz_table

  as_tibble(tz_table, format = 'pipe') -> tz_tibble

as_kable_extra(tz_table, format = "latex",booktabs = T) -> tz_kable

```{r tzTabPrint, results='asis'}

tz_kable %>% kable_styling(latex_options = c("scale_down"))
